Title goes here

### 2016-10-23 paper/paper.tex
Added introduction

@@

Most of aircraft are provided with ADB-S transmitter, which send continuosly information about the status and the position of the aircraft to guarantee better air traffic control. The messages are not encripted end, in most region, this technology will become mandatory in 2020. For these reasons OpenSky network was recently born.

>>>>

The number of flying airplane has increased much in the last decade. This led to many problems, mostly related to security and air traffic controls. It was clear that radar surveillance systems would not be sufficient to monitor flights, since airplanes are passive entity. With the introduction of new technologies, a new standard called ADS-B has been developed to actively monitor aircrafts and manage routings.

\textit{Automatic Dependant Surveillance - Broadcast} (ADS-B) is the last generation standard for air traffic monitoring. The main idea of this technology is that each aircraft broadcast its position and status using internal sensors, without relying on external entities. On the other side, each airplane is able to receive the messages and detect the position of other vehicle autonomously, thus maintening a minimum distance and avoiding collision.

ADS-B messages are sent without any encryption and can be received and decoded by everyone. Morover this equipment will be mandatory in 2017 in most countries. We obtained a dataset, provided by OpenSky network, containing all the ADS-B messages sent by airplanes and collected by volunteers. The dataset includes data about flights from the 18\textsuperscript{th} September 2016 to the 24\textsuperscript{th} September 2016 and collected by about 70 sensors spread across Europe.

In this paper we explain our analysis of such dataset, starting from the decoding of the position. The main goals of this project are:
\begin{itemize}
  \item Detecting the standard routes between all the pairs of airports;
  \item Detecting abnormal routes between pairs of airports;
  \item Calculate the wastage of fuel travelling through the standard route instead of flying over a straight line.
\end{itemize}

We will show that, though most standard routes are really close to the straight line, there are some routes that are clearly away from it. Moreover, for some couples of airports, there are few routes that differ from the standard one.

@@

Most of aircraft are provided with ADB-S transmitter, which send continuosly information about the status and the position of the aircraft to guarantee better air traffic control. The messages are not encripted and, in most region, this technology will become mandatory in 2020. For these reasons OpenSky network was recently born.
